### 2015-05-15 background.tex
fix

The most common method for avoiding races is by protecting sets of program statements that access a shared resource with \emph{locks}, forming \emph{critical sections}.  Figure~\ref{fig:lock_example} shows how to use locking to eliminate the races in Figure~\ref{fig:data_race_example}. Because the \texttt{return} statement can potentially race on the \texttt{f\_pos} field, we store the result in a temporary variable inside the critical section.
%
Careless use of locks has many well-known pitfalls~\cite{sutter2005software}: coarse-grained locking can hurt performance, as it limits the opportunity for concurrency; while fine-grained locking can easily lead to deadlocks. Although the Linux kernel provides sophisticated lock-free synchronization mechanisms~\cite[p.\ 123]{corbet2005linux}, such as atomic read-modify-write operations, in this work we focus on locks as they are widely used.\footnote{We treat lock-free operations soundly, by not regarding them as providing any protection between threads, but this can lead to false alarm race reports.}

>>>>

The most common method for avoiding races is by protecting sets of program statements that access a shared resource with \emph{locks}, forming \emph{critical sections}.  Figure~\ref{fig:lock_example} shows how to use locking to eliminate the races in Figure~\ref{fig:data_race_example}. Because the \texttt{return} statement can potentially race on the \texttt{f\_pos} field, we store the result in a temporary variable \texttt{res} inside the critical section.
%
Careless use of locks has many well-known pitfalls~\cite{sutter2005software}: coarse-grained locking can hurt performance, as it limits the opportunity for concurrency; while fine-grained locking can easily lead to deadlocks. Although the Linux kernel provides sophisticated lock-free synchronization mechanisms~\cite[p.\ 123]{corbet2005linux}, such as atomic read-modify-write operations, in this work we focus on locks as they are widely used.\footnote{We treat lock-free operations soundly, by not regarding them as providing any protection between threads, but this can lead to false alarm race reports.}
